Data Exploration

### 2021-10-09 code/processing_code/Data_Exploration.Rmd
Project Part 2 - CC

#### Loading the data from the processing script. Note that because you are loading a library at the beginning, it may either take a while or take several tries.
```{r}
MIDO <- readRDS("../../data/processed_data/MIDO.rds")
NORO <- readRDS("../../data/processed_data/NORO.rds")
BICO <- readRDS("../../data/processed_data/BICO.rds")
```
 <- source("processingscript.R", local = knitr::knit_global())

>>>>

#### Loading the data from the processing script. Note that because you are loading a library at the beginning, it may either take a while or take several tries.
```{r}
MIDO <- readRDS("../../data/processed_data/MIDO.rds")
NORO <- readRDS("../../data/processed_data/NORO.rds")
BICO <- readRDS("../../data/processed_data/BICO.rds")
```
